Eliminating Input-Based Attacks by Deriving Automated Encoders and Decoders from Context-free Grammars

### 2024-11-22 paper.tex
Fix authors

\author{\IEEEauthorblockN{Tobias Bieschke\textsuperscript{1},
Lars Hermerschmidt\textsuperscript{1,2},
Bernhard Rumpe\textsuperscript{1} and
Peter Stanchev\textsuperscript{1}}
\IEEEauthorblockA{Software Engineering, RWTH Aachen University, Germany\textsuperscript{2}\\
AXA Konzern AG, Germany\textsuperscript{2}
%Email: tobias.bieschke@rwth-aachen.de, hermerschmidt@se-rwth.de, rumpe@se-rwth.de, peter.stanchev@rwth-aachen.de}
}
}

>>>>

\author{\IEEEauthorblockN{
Lars Hermerschmidt\textsuperscript{1} and
Mark Vollmary\textsuperscript{2}}
\IEEEauthorblockA{REWE digital, Germany\textsuperscript{1}\\
AXA Konzern AG, Germany\textsuperscript{2}}
}
